Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-13 paper/sec-analysis.tex
work in the paper

In section we describe our analysis strategy, and in particular
the classification of each individual event into
different categories according to the event topology.
%
First of all we discuss the settings and nomenclature that
we will use for jet clustering in this work.
%
Then we move to discuss how $b$-tagging is simulated,
following closely the ATLAS techniques.
%
Then we discuss the categorisation of events between different
topologies, and how we can prioritise among them.

@@

In our study we will use different types of jet definitions,
depending of the type of analysis that needs to be performed, optimized
for the various possible event topologies.
%
Therefore, we being by enumerating the choices that we make.
%
The starting point after the parton shower is the clustering
of all final state particles.
%
In this work all the jet reconstruction algorithms
are obtained from the {\tt FastJet} program~\cite{Cacciari:2011ma},
v3.1.0.
%
We adopt the following terminology for the different types of jets
that we will use in this work:

@@

  These are jets  reconstructed with the
  anti-$k_T$ clustering algorithm~\cite{Cacciari:2008gp} with $R=0.4$ radius.
  %
  When reconstructing small-$R$ jets, we will keep only
  those jets with transverse momentum $p_T \ge 40$~GeV
  and pseudo-rapidity $|\eta|<2.5$ within the central
  acceptance of ATLAS and CMS, jets that fail to satisfy these
  conditions are discarded.
  %

@@

  These jets are also constructed with the
  anti-$k_T$ clustering algorithm, now using a $R=1.0$ radius.
  %
  In order to be accepted, these large-$R$ jets should
  satisfy  $p_T \ge 200$~GeV and lie in a pseudo-rapidity range by
  $|\eta|<2.0$.
  %
  If these conditions are not satisfied, the jet is discarded.
  %
  The more restrictive range  in pseudo-rapidity
  as compared to the small-$R$ jets,
  is motivated by mimicking the  experimental requirements
  in ATLAS and CMS
  related to the track-jet-based calibration.

@@

  Once we have reconstructed a suitable large-$R$ jet, important
  information can be obtained by looking at the kinematics of
  the small-$R$ subjets.
  %
  These subjets will be obtained by reclustering the constituents
  of the large-$R$ jet, always with the  anti-$k_T$ algorithm,
  but this time with a smaller radius parameter $R=0.3$.
  %
  As we will discuss below, these small-$R$ subjets are the key of
  the $b$-tagging in the boosted category.
  %
  Small-$R$ subjets are required to have $p_T > 50$~GeV and $|\eta|<2.5$,
  else they are discarded.

@@

Given the final state that needs to be reconstructed in our case, the
optimisation of the $b$-tagging capabilities of the
LHC experiments is an essential requirement to optimise
the prospects for the observation of Higgs pair production.
%
The $b$-tagging used in this feasibility study is inspired
in the current and projected ATLAS settings, and below
we also comment on the differences and similarities with the
corresponding CMS strategy~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}.
%
For each type of jet defined above, a different
$b$-tagging strategy is used, as we discuss now.

@@

  These are $b$-tagged as follows.
  %
  If a small-$R$ jet has at least one $b$-quark among their constituents,
  it will be tagged as a $b$-jet with probability $f_b$.
  %
  If no $b$-quarks are found among the constituents
  of this jet, it can be still be tagged as a $b$-jet with
  a mistag rate of $f_l$.
  %
  Note that the probability of tagging a jet is not modified
  if more than one $b$-quark is found among the jet constituents.

  We only attempt to $b$-tag the four (two) hardest small-$R$ jets
  in the resolved (intermediate) category.
  %
  We find that
  trying to $b$-tag all
  small-$R$ jets that satisfy the acceptance cuts worsens the performance
  due to combinatorics.

@@

    Large-$R$ jets are $b$-tagged by ghost-associating anti-$k_T$ $R=0.3$
    subjets (defined as above) to the original large-$R$ jets.
    %
    In particular,
    a large-$R$ jet is considered  double-$b$-tagged if both
    the leading and subleading subjets (where the ordering
    is done in the subjet $p_T$) are both individually $b$-tagged.
    %
    Note that we only attempt to $b$-tag the two leading subjets:
    trying to $b$-tag all subjets above the $p_T$ cut degrades
    the signal significance due to the increase in combinatorics.

    Therefore, in this work we will exploit the capabilities of
    the LHC experiment of double-$b$-tagging inside large-$R$ jets.
    %
    Below we comment on the dependence of our results if single-$b$-tagging
    would be performed also for the large-$R$ jets, as done
    for the small-$R$ jets.

@@

Concerning the actual values of the $b$-tag probability $f_b$ and
the $b$-mistag probability of light jets $f_l$, in this work
we adopt as baseline the values $f_b=0.8$ and $f_l=0.01$.
%
In Sect.~\ref{sec:optimisation} we study the dependence of
our results against variations of $f_b$ and $f_l$ both
using more conservative and more aggressive values.
%
There we also study the dependence of the results
on other analysis settings related to the performance of
the experiments, for example by varying the momentum smearing.

\subsection{Event categorisation and cut flow}
\label{sec:categorisation}

After having introduced the types of jet reconstruction
that we will use, as well as the $b$-tagging strategy,
we need to discuss the analysis strategy, including
the event categorization and the cut flow.

The basic idea of this work is similar to that in Ref.~\cite{Gouzevitch:2013qca}:
rather than concentrating only a specific event topology, such as boosted
or resolved, we aim to consistently combine the information from
the three possible event topologies: boosted, intermediate and
resolved, which we define now.
%
An important difference as compared to~\cite{Gouzevitch:2013qca}
is that here each category is optimised separately, and then
a exclusive categorisation is defined starting from the topology
where the signal significance is the best.

Let us therefore define the three event categories that
we use in this work:
\begin{itemize}
\item {\it Boosted category}.

  A given event is assigned to the {\it boosted} category if it
  contains at least two large-$R$ jets, defined as above,
  and where  the two leading large-$R$ jets have been
  successfully double-$b$-tagged.
  %
 Therefore, each of these two large-$R$ double-$b$-tagged jets corresponds to the
 decay products of one Higgs boson candidate.

@@

  An event is assigned to the {\it intermediate} category if
  at least one large $R$ double-$b$-tagged jet is present.
  %
  If more than one is found, then the leading large-$R$ jet
  is assigned to be the first Higgs candidate.
  %
  In addition, we require at least two small-$R$ jets,
  which must be separated with respect to the large-$R$
  jet by at least an angular separation of $\Delta R\ge 1.0$.
  %
  These small-$R$ jets must be $b$-tagged as well.

  Then, the second Higgs boson candidate is reconstructed
  by selecting the two $b$-tagged small-$R$ jets that minimize the difference
  between the invariant mass of the large-$R$ jet, $m_{lR_1}$,
  with the invariant mass of the sum of the two small-$R$ jets,
  $m_{sR_1+sR_2}$, that is, ${\rm min}\lp m_{lR} -
  m_{sR_1+sR_2}\rp$, where $lR_1$ indicates the leading large-$R$ jet
  and $sR_1$ and $sR_2$ indicate the small-$R$ jets.m

\item {\it Resolved category}.

  Finally, let us define the {\it resolved} category.
  %
  An event is assigned to this category
  if at least
  four $b$-tagged small-$R$ jets are present.
  %
  The two Higgs candidates are then reconstructed out of the
  leading four small-$R$ jets in the event
  by considering all possibilities of forming two pairs of jets
  with invariant masses $m_{sR_1+sR_2}$ and 
$m_{sR_3+sR_4}$, respectively, and choosing the configuration that minimizes their difference $|m_{sR_1+sR_2} - m_{sR_3+sR_4}|$. 
  %
  The requirement of restricting this selection to only the four
  leading small-$R$ jets arises from the need to reducing the
  combinatorics from the fakes.
\end{itemize}
Note that in principle these three categories are not exclusive:
a given even can be assigned to more than one category, for
example, satisfying both the requirements of the boosted and resolved
categories at the same time.

Once a pair of Higgs boson candidates has been identified,
then events from each category are required to satisfy the usual
Higgs mass window cut, defined by
the following condition
\be
\label{higgsmasswindow}
|m_{h,j} - 125| < 40~{\rm GeV} \, , j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of the two Higgs candidates
reconstructed as explained above.
%
We note that this cut is substantially looser as the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
for this is that the MVA will take care of the optimisation of these
and other cuts that are not explicitly performed.

In Table~\ref{sec:categorisation} we summarize the definitions of each
category.
%
We emphasize again that each category is not exclusive of the others,
and in general there can be a substantial overlap
between the different categories.
%
In particular, this overlap is a direct consequence that
the different categories are optimised separately, as opposed
to the approach of~\cite{Gouzevitch:2013qca}, where optimisation
was performed simultaneously in the combination of exclusive categories.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \small
  \begin{tabular}{c|c|c|c}
    \hline
    &  Boosted  &  Intermediate  &  Resolved  \\
    \hline
    \hline 
    Jet selection  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
    jets  &  $\ge$ 4 small-$R$ jets \\
    \hline
    Jet cuts  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
    &  $p_T \ge 40$ GeV \\
    &  & $p_T \ge 40$ GeV (small-$R$ jets)   &    \\
    &   $|\eta|<2.0$  & $|\eta|<2.0$ (large-$R$ jet) & $|\eta|<2.5$ \\
    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\
    \hline
    $b$-tagging  & 2 double-$b$-tags  & 1 double-$b$-tag & 4 single-$b$-tags \\
    &  & and 2 single-$b$-tags  &  \\
       & $\ge 2$ small-$R$ subjets  & &  \\
    &  $p_T^{\rm sj}\ge 50$ GeV &   &  \\
    \hline
    \end{tabular}
  \caption{\small Definition of the three event categories used in this
    work, together with the corresponding basic kinematical cuts.
    %
    The categories are not exclusive, and each event can satisfy the
    requirements of more than one category at the same time.  
\label{sec:categorisationTable}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As we will show now, the selection requirement and the kinematic cuts
for each of the categories in Table~\ref{sec:categorisationTable} have
been optimised independently.
%
First of all we have performed a inclusive analysis, and optimised
$S/\sqrt{B}$ in each of the three categories separately, including
the MVA.
%
We find that, in terms of signal significance, the ordering of
the categories is
\begin{enumerate}
\item Boosted 
\item Intermediate
  \item Resolved
  \end{enumerate}
and therefore for the final analysis we turn to an exclusive approach:
if an event satisfies the boosted requirements, it is kept for
these category, else we check if it suits the intermediate
requirements, and failing also this, the event is attempted
in the resolved categories.
%
The resulting exclusive event samples are then separately processes
through the MVA, as discussed in the next section.
%
This allows us to combine the significance of the dominant topology
(boosted) with that of the sub-leading categories, intermediate
and resolved.

\subsection{Cut optimisation}

In this section we motivate the various
kinematical cuts applied to the different categories.
%
These cuts have been separately
optimised in an inclusive analysis, since it is only
once we have determined
the dominant category that the analysis is made exclusive.
%
Here we show the various kinematic distributions immediately
below the corresponding cut has been applied.
%
Only a representative subset of
all available kinematic distributions will be shown here, the complete
set of plots, including the distribution of all substructure
variables used in the MVA later, have been collected
in this webpage:
\begin{center}
\url{http://www2.physics.ox.ac.uk/HH4b}
  \end{center}
In this section we restrict to the discussion of the
kinematic distributions of the boosted
and resolved categories, the corresponding results for the
intermediate category are collected in the same webpage.

@@

In the intermediate category,
it is important to understand the $p_T$ distribution
of the four leading small-$R$ jets of the event.
%
Given that in general the boost from the Higgs decays is moderate,
the two subleading jets might be not too hard, and thus it
should be important to ensure that our $p_T^{\rm min}$ cut
is not too strong.
%
This also has important implications for the experimental
trigger requirements in this category.
%
In Fig. we show the distribution in $p_T$ of the four leading
small-$R$ jets in signal and background events.
%
We see that the third and four leading jets are relatively soft.
%
Therefore, we can conclude that....

@@

Next in Fig.~\ref{fig:mHHinv} we show the invariant mass
of the leading reconstructed Higgs candidates, before the Higgs mass window
cut is applied, for the resolved and boosted categories.
%
The signal distribution is of course peaked at the
nominal Higgs mass of $m_h=125$ GeV.
%
In the boosted category, the background shows no particular
structure, while remarkable in the resolved category the background
also shows a peak-like structure, artificially induced by the
acceptance kinematical cuts on the jets.
%
Note that the applied smearing, which mimics detector resolution effects,
leads to a rather broad distribution which reduces the usefulness
of the Higgs mass window cut.
%
While our Higgs mass window cut is relatively loose,
information of the different shape of the $m_{h}$
distribution will still be exploited by the MVA.
%
In Sect.~\ref{sec:optimisation} we discuss how the results
of the analysis is modified if a more aggressive
detector resolution is assumed (corresponding
to a smaller value of the smearing).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1.pdf}
  \includegraphics[width=0.48\textwidth]{plots/m_H0_boost_C1.pdf}
  \caption{\small The invariant mass distribution of the leading
    Higgs candidates on the resolved (left plot) and boosted (right
    plot) categories.
}
\label{fig:mHHinv}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

In the resolved case, we see that the distribution
in $m_{hh}$ is rather harder for the signal as for the background,
and thus one expects that cutting in $m_{hh}$ would help signal
discrimination: we will verify this with the help of the MVA.
%
For the boosted category the trend of the $m_{hh}$ distribution
is different because of the jet selection cuts, with the
distribution now peaking at higher values.
%
In this case signal and background distributions
look reasonably similar.
%
Note that at parton-level the $m_{hh}$ distribution as a kinematical
cut-off at $m_{hh}^{\rm min}=250$ GeV, which is modified by both
shower effects and by detector resolution effects.
%
While we don't cut in this quantity, it is
one of the inputs for the MVA to help to improve signal discrimination.

@@

Another interesting distribution is the transverse momentum of
the di-Higgs system.
%
In Fig.~\ref{fig:pthh} we show the $p_T^{hh}$
distribution
for the resolved and boosted categories.
%
Note that in our LO simulation this distribution is generated purely
by the parton shower - a more refined calculation would require
either the matching with higher-multiplicity matrix elements~\cite{Maierhofer:2013sha} or
the full NLO calculation~\cite{Frederix:2014hta}, to treat properly the first hard emission.
%
Again we see that the background has a steeper $p_T^{hh}$ distribution
that the signal, in both categories, thus this variable
should provide some additional discrimination power, and therefore
we will use it as another of the MVA inputs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.48\textwidth]{plots/pt_HH_res_C1.pdf}
  \includegraphics[width=0.48\textwidth]{plots/pt_HH_boost_C1.pdf}
  \caption{\small Left plot: the invariant mass distribution of the Higgs
    pair candidates, $m_{hh}$, comparing signal and background events,
    in the resolved category.
    %
    Right plot: same for the boosted category.
}
\label{fig:pthh}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In section we describe our analysis strategy, and in particular
the classification of each individual event into
different categories according to its topology.
%
First of all we discuss the settings and nomenclature that
we will use for jet clustering, and then we move to discuss how $b$-tagging is simulated.
%
Then we discuss the categorisation of events between different
topologies, and how we prioritise among them.
%
Finally, we motivate our choice of analysis cuts by comparing signal and background
for the relevant kinematic distributions.

@@

The starting point after the parton shower is the clustering
of all final state particles using the
jet reconstruction algorithms
are obtained from the {\tt FastJet} program~\cite{Cacciari:2011ma},
v3.1.0.
%
In our study use different types of jet definitions,
which we enumerate now:
%

@@

  These are jets  reconstructed with the
  anti-$k_T$ clustering algorithm~\cite{Cacciari:2008gp} with $R=0.4$ radius.
  %
  When reconstructing small-$R$ jets, we keep only
  those jets with transverse momentum $p_T \ge 40$~GeV
  and pseudo-rapidity $|\eta|<2.5$ within the central
  acceptance of ATLAS and CMS.
%
  Jets that fail to satisfy these acceptance
  requirements are discarded.
  %
  The restriction to the central rapidity region is a
  requisite for $b$-tagging.

@@

  These jets are also constructed with the
  anti-$k_T$ clustering algorithm, now using a $R=1.0$ radius.
  %
  In order to be accepted, these large-$R$ jets should
  satisfy  $p_T \ge 200$~GeV and lie in a pseudo-rapidity range by
  $|\eta|<2.0$.
  %
  If these conditions are not satisfied, the jet is discarded.
  %
  The more restrictive range  in pseudo-rapidity
  as compared to the small-$R$ jets
  is motivated by mimicking the  experimental requirements
  in ATLAS and CMS
  related to the track-jet-based calibration~\cite{Aad:2014bia,ATLAS:2012kla}.

@@

  Once we have reconstructed a suitable large-$R$ jet, important
  information can be obtained by looking at the kinematics of
  the small-$R$ subjets.
  %
  These subjets will be obtained by reclustering the constituents
  of the large-$R$ jet, always with the  anti-$k_T$ algorithm,
  but this time with a smaller radius parameter $R=0.3$.
  %
  These small-$R$ subjets will be the input of
  the $b$-tagging in the boosted category.
  %
  Small-$R$ subjets are required to have $p_T > 50$~GeV and $|\eta|<2.5$,
  else they are discarded.
  %
\end{itemize}

Let us mention that we explored the possible improvements
in the analysis from using variable-$R$ jets~\cite{Krohn:2009zg}, but found that these made
a small difference as compared to fixed-$R$ jets.
%
This is not unexpected, since variable-$R$ jets are more suitable when
the degree of boost of the final state being reconstructed can span
a wide range, such as in heavy resonance searches~\cite{Aad:2015fna}.

@@

Given the $4b$ final state that needs to be reconstructed, the
optimisation of the $b$-tagging capabilities of the
LHC experiments is an essential requirement to improve
the prospects for the observation of Higgs pair production in this channel.
%
The $b$-tagging used in this feasibility study is inspired
in the current and projected ATLAS settings~\cite{Aad:2013gja},
though
it is not too different from
 the corresponding CMS strategy~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}.
%
For each type of jet defined above, a different
$b$-tagging strategy is used:

@@

  These are $b$-tagged as follows.
  %
  If a small-$R$ jet has at least one $b$-quark among their constituents,
  it will be tagged as a $b$-jet with probability $f_b$.
  %
  If no $b$-quarks are found among the constituents
  of this jet, it can be still be tagged as a $b$-jet with
  a mistag rate of $f_l$.
  %
  The probability of tagging a jet is not modified
  if more than one $b$-quark is found among the jet constituents.

  We only attempt to $b$-tag the four (two) hardest small-$R$ jets
  in the resolved (intermediate) category.
  %
  We find that
  attempting to $b$-tag all
  small-$R$ jets that satisfy the acceptance cuts worsens the performance
  due to combinatorics after the parton shower.

@@

    Large-$R$ jets are $b$-tagged by
    ghost-associating anti-$k_T$ $R=0.3$
    subjets to the original large-$R$
    jets~\cite{Cacciari:2007fd,Aad:2013gja,
      ATLAS-CONF-2014-004}.\footnote{The same
    method was used in the recent ATLAS $hh\to 4b$ search~\cite{Aad:2015uka}.}
    %
    In particular,
    a large-$R$ jet is considered  double-$b$-tagged if both
    the leading and subleading subjets (where the ordering
    is done in the subjet $p_T$) are both individually $b$-tagged.
    %
    Note that we only attempt to $b$-tag the two leading subjets:
    trying to $b$-tag all subjets above the $p_T$ cut degrades
    the signal significance due to the increase in combinatorics.

@@

Concerning the actual values of the $b$-tag probability $f_b$ and
the $b$-mistag probability of light jets $f_l$, 
we adopt as baseline the values $f_b=0.8$ and $f_l=0.01$.
%
In Sect.~\ref{sec:optimisation} we study the dependence of
our results against variations of $f_b$ and $f_l$ both
using more conservative and more aggressive values.
%

\subsection{Event categorisation}
\label{sec:categorisation}

The basic idea of our analysis strategy is similar to that in Ref.~\cite{Gouzevitch:2013qca}:
rather than concentrating only a specific event topology, such as boosted
or resolved, we aim to consistently combine the information from
the three possible event topologies: boosted, intermediate and
resolved.
%
An important difference as compared to~\cite{Gouzevitch:2013qca}
is that here each category is optimised separately, and then
a exclusive categorisation is defined starting from the category
with the highest signal significance.
%
An advantage of our approach is that the analysis strategy would be unchanged
if the underlying production model is varied, for example in the case of
BSM dynamics.

Let us therefore define the three event categories that
we use:
\begin{itemize}
\item {\it Boosted category}.

  An event is assigned to the {\it boosted} category if it
  contains at least two large-$R$ jets, defined as above,
  and where  the two leading large-$R$ jets have been
   double-$b$-tagged.
  %
 Therefore, each of these two large-$R$ double-$b$-tagged jets corresponds to the
 decay products of one Higgs boson candidate.

@@

  An event is assigned to the {\it intermediate} category if
  one and only one large $R$ double-$b$-tagged jet is present,
  which corresponds to the the first Higgs candidate.
  %
  In addition, we require at least two small-$R$ jets,
  which must be separated with respect to the large-$R$
  jet by at least an angular separation of $\Delta R\ge 1.0$.
  %
  These small-$R$ jets must be $b$-tagged as well.

  The second Higgs boson candidate is reconstructed
  by selecting the two $b$-tagged small-$R$ jets that minimize the difference
  between the invariant mass of the large-$R$ jet, $m_{lR_1}$,
  with the invariant mass of the sum of the two small-$R$ jets,
  $m_{sR_1+sR_2}$, that is, ${\rm min}\lp m_{lR} -
  m_{sR_1+sR_2}\rp$, where $lR_1$ indicates the leading large-$R$ jet
  and $sR_1$ and $sR_2$ indicate the small-$R$ jets.

\item {\it Resolved category}.
  %
  An event is assigned to the {\it resolved} category
  if at least
  four $b$-tagged small-$R$ jets are present.
  %
  The two Higgs candidates are then reconstructed out of the
  leading four small-$R$ jets in the event
  by considering all possibilities of forming two pairs of jets
  with invariant masses $m_{sR_1+sR_2}$ and 
$m_{sR_3+sR_4}$, respectively, and choosing the configuration that minimizes their difference $|m_{sR_1+sR_2} - m_{sR_3+sR_4}|$. 
  %
  The requirement of restricting this selection to only the four
  leading small-$R$ jets arises from the need to reducing the
  combinatorics from the fakes.
\end{itemize}
Note that these three categories are not exclusive:
a given even can be assigned to more than one category, for
example, satisfying both the requirements of the boosted and resolved
categories at the same time.
%
The exception is the boosted and intermediate categories, which have
orthogonal jet selection requirements.

Once a Higgs boson candidate has been identified,
its invariant mass is required to be within a fixed window
around the nominal Higgs boson mass.
%
In particular we require the condition
\be
\label{higgsmasswindow}
|m_{h,j} - 125| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of each of the two reconstructed  Higgs candidates.
%
This cut is substantially looser as the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
for this choice is that the MVA will take care of the optimisation of these
and other cuts that are not explicitly performed.
%
Only events where the two Higgs candidates satisfy the
condition in Eq.~(\ref{higgsmasswindow}) are classified as signal events.

In Table~\ref{sec:categorisation} we summarize the definitions of each
category.
%
We emphasize again that each category is not exclusive,
and in general there will be a substantial overlap
between the different categories.
%
This overlap is a direct consequence that
the different categories are optimised separately.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \small
  \begin{tabular}{c|c|c|c}
    \hline
    &  Boosted  &  Intermediate  &  Resolved \\
    \hline
    \hline 
    Jet selection  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
    jets  &  $\ge$ 4 small-$R$ jets \\[0.2cm]
    \hline
    Jet cuts  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
    &  $p_T \ge 40$ GeV \\
    &  & $p_T \ge 40$ GeV (small-$R$ jets)   &    \\
    &   $|\eta|<2.0$  & $|\eta|<2.0$ (large-$R$ jet) & $|\eta|<2.5$ \\
    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\[0.2cm]
    \hline
    $b$-tagging  & 2 double-$b$-tags  & 1 double-$b$-tag & 4 single-$b$-tags \\
    &  & and 2 single-$b$-tags  &  \\
    & and $\ge 2$ small-$R$ subjets  &  and $\ge 2$ small-$R$ subjets  &  \\
     &  in large-$R$ jets  &  in large-$R$ jet &  \\
    &  $p_T^{\rm sj}\ge 50$ GeV & $p_T^{\rm sj}\ge 50$ GeV   &  \\[0.2cm]
    \hline
    Mass-Drop Tag  &  Two leading large-$R$ jets  &  Large-$R$ jet &   \\
    \hline
    \end{tabular}
  \caption{\small Definition of the three event categories used in this
    work, together with the corresponding basic kinematical cuts.
    %
    The categories are not exclusive, and each event can satisfy the
    requirements of more than one category at the same time.  
\label{sec:categorisationTable}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The selection requirements and the kinematic cuts
for each of the categories in Table~\ref{sec:categorisationTable} have
been optimised independently.
%
First of all we have performed a inclusive analysis, and optimised the
signal significance
$S/\sqrt{B}$ in each of the three categories separately, including
the MVA.
%
We find that the category with higher significance turns out to be the boosted,
followed by the intermediate and the resolved ones.
%
Therefore for the final analysis we turn to an exclusive approach:
if an event satisfies the boosted requirements, it is kept for
these category, else we check if it suits the intermediate
requirements, and failing also this, the event is attempted to
be classified in the
resolved category.
%
The resulting exclusive event samples are then separately processes
through the MVA.
%
This allows us to combine the significance of the dominant topology
(boosted) with that of the sub-leading categories, intermediate
and resolved, without the problem of the double counting.

\subsection{Optimisation of kinematical cuts}

We now motivate the values of
kinematical cuts applied to the different categories.
%
These cuts have been separately
optimised in an inclusive analysis, since it is only
once we have determined
the dominant category that the analysis is made exclusive.
%
Here we show the various kinematic distributions 
before the corresponding cut has been applied.
%
For illustration purposes,
only a representative subset of
all available kinematic distributions will be shown here.
%
For simplicity,
we restrict to the discussion of the
kinematic distributions of the boosted
and resolved categories.

@@

In the resolved category,
it is important to understand the $p_T$ distribution
of the four leading small-$R$ jets of the event.
%
As noted in~\cite{deLima:2014dta}
given that in general the boost from the Higgs decays is moderate,
the two subleading jets might be not too hard, and thus it
should be important to ensure that our $p_T^{\rm min}$ cut
is not too strong.
%
This also has important implications for the experimental
trigger requirements in this category.
%
In Fig. we show the distribution in $p_T$ of the four leading
small-$R$ jets in signal and background events.
%
We see that the third and four leading jets are relatively soft.
%
Therefore, we can conclude that....

@@

Next, in Fig.~\ref{fig:mHHinv} we show the invariant mass
of the leading reconstructed Higgs candidates, before the Higgs mass window
cut Eq.~(\ref{higgsmasswindow})
  is applied, for the resolved and boosted categories.
%
The signal distribution is of course peaked at the
nominal Higgs mass of $m_h=125$ GeV.
%
In the boosted category, the background shows no particular
structure, while remarkable in the resolved category the background
also shows a peak-like structure, artificially induced by the
acceptance kinematical cuts on the jets.
%
Note that the applied smearing, which mimics detector resolution effects,
leads to a rather broad distribution which reduces the usefulness
of the Higgs mass window cut.
%
While our Higgs mass window cut is relatively loose,
information of the different shape of the $m_{h}$
distribution will still be exploited by the MVA.
%
In Sect.~\ref{sec:optimisation} we discuss how the results
of the analysis is modified if a more aggressive
detector resolution is assumed (corresponding
to a smaller value of the smearing).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1.pdf}
  \includegraphics[width=0.48\textwidth]{plots/m_H0_boost_C1.pdf}
  \caption{\small The invariant mass distribution of the leading
    Higgs candidates on the resolved (left plot) and boosted (right
    plot) categories. {\bf redo boosted case with correct axes range}
}
\label{fig:mHHinv}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

In the resolved case, we see that the distribution
in $m_{hh}$ is rather harder for the signal as for the background,
and thus one expects that cutting in $m_{hh}$ would help signal
discrimination: we will verify this with the help of the MVA.
%
For the boosted category the trend of the $m_{hh}$ distribution
is different because of the jet selection cuts, with the
distribution now peaking at higher values.
%
In this case signal and background distributions
look reasonably similar.
%
Note that at parton-level the $m_{hh}$ distribution as a kinematical
cut-off at $m_{hh}^{\rm min}=250$ GeV, which is modified by both
shower effects and by detector resolution effects.
%
While we don not cut in this quantity, it is
one of the inputs for the MVA to help to improve signal discrimination.

@@

Another interesting distribution is the transverse momentum of
the di-Higgs system.
%
In Fig.~\ref{fig:pthh} we show the $p_T^{hh}$
distribution
for the resolved and boosted categories.
%
Again we see that the background has a steeper $p_T^{hh}$ distribution
that the signal, in both categories, thus this variable
should provide some additional discrimination power, and therefore
we will use it as another of the MVA inputs.
%
Note that in our LO simulation this distribution is generated purely
by the parton shower - a more refined calculation would require
either the matching with higher-multiplicity matrix elements~\cite{Maierhofer:2013sha} or
the full NLO calculation~\cite{Frederix:2014hta}, to treat properly the first hard emission.
%
Nevertheless, the MVA shows only limited sensitivity to this variable, so its
modelling appears not to be crucial in our case.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.48\textwidth]{plots/pt_HH_res_C1.pdf}
  \includegraphics[width=0.48\textwidth]{plots/pt_HH_boost_C1.pdf}
  \caption{\small Same as Fig.~\ref{fig:mhh} for the transverse momentum
    distribution of the di-Higgs system $p_T^{hh}$.
}
\label{fig:pthh}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
